The Augmented Joint-space Task-oriented Dynamical System

### 2018-02-22 paper/old-iterations/main_v10.tex
Latest changes

\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{url}
\usepackage[font={footnotesize}]{caption}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[usenames, dvipsnames]{color}
\usepackage{amsmath}
\renewcommand{\labelenumii}{\Roman{enumii}} 
\usepackage{authblk}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[hidelinks]{hyperref}
% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

\usepackage{xcolor,colortbl}

\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
\definecolor{Gray}{gray}{0.85}
\definecolor{LightCyan}{rgb}{0.88,1,1}

\let\labelindent\relax
\usepackage{enumitem}
\usepackage{dsfont}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Learning Joint-Space Stable Dynamical Systems for Task-Space Objectives}
\title{Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A
Linear Parameter Varying and Synergetic Control Approach}

%OR
%\title{Learning Augmented Joint-Space Task-Oriented \\ Dynamical Systems in Synergy Space}

%
%
\author{Yonadav~Shavit*,  Seyed~Sina~Mirrazavi~Salehian*, Nadia~Figueroa*, Aude~Billard
% <-this % stops a space
\thanks{*These authors contributed equally to this work.}
\thanks{Y. Shavit is with the Department
of Electrical Engineering and Computer Science, Massachusetts Institute of Technology, Cambridge,
MA, 02139 USA. E-mail: yonadav.shavit@gmail.com.}% <-this % stops a space
\thanks{S. S. M. Salehyan, N. Figueroa, and A. Billard are with the Swiss Federal Institute of Technology (EPFL), 1015 Lausanne, Switzerland. \\E-mail: \{sina.mirrazavi,nadia.figueroafernandez,aude.billard\}@epfl.ch.}
}% <-this %

@@

\begin{abstract}
In this paper, we propose a stable joint-space dynamical system that captures desired behaviors in joint-space while converging towards a reachable target in task-space. Our method is fast to compute and smoothly moves through classic kinematic singularities by avoiding the use of the pseudo-inverse Jacobian; moreover, it Lyapunov-stably converges towards its task-space attractor. To encode complex joint-space behaviors while meeting these stability criteria, the dynamical system is constructed as a Linear Parameter Varying (LPV) system combining different motor synergies, and we provide a method for learning these synergy matrices from demonstrations. Specifically, we use dimensionality reduction to find low-dimensional synergy regions, and then estimate the parameters of the corresponding synergies by solving a convex semi-definite optimization problem that minimizes the joint velocity prediction error from the demonstrations. Our proposed approach is validated on a variety of motions for a 7-DOF KUKA LWR4+ robot arm.\end{abstract}

@@

\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:intro}
\textcolor{red}{We'll remove the subsection headings later..\\ Some comments:\\- Change PbD to LfD everywhere}
\subsection{\textcolor{red}{Motivation for learning joint+task-space behaviors}}
\textcolor{red}{*See comments in tex*}
% % TO YO: OUTLINE FOR RE-WRITING THIS PART
%1. Start with motivation of LfD  
%2. Mention that we can learn behaviors in either joint or task space 
%3. briefly summarize the approaches in each without going into detail; i.e. probabilistic models, DS, etc 
%4. Motivate why we want to learn behaviors in joint+task space: 1 is because of the implications of IK as we already discuss, 2 to mimic joint trajectories.. here give your example of why we would want that and mention applications such as table tennis[1], grasping[2] and bi-manual coordination [3].
%
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.16,trim={0 0 0 0cm},clip]{Without_Obstcle_white_new.png}\includegraphics[scale=.135,trim={0 0 0 0cm},clip]{With_Obstcle.png}
\caption{Two robot motions in \textcolor{orange}{\textbf{joint-space}} accomplishing \textit{similar} behavior in \textcolor{cyan}{\textbf{task-space}} (pouring chips in a bowl). The left example avoids a known obstacle in its workspace, while the right one does not.}
\label{fig:robot_example}
\vspace{-15pt}
\end{figure}

@@

Although DS-based task-space learning techniques ensure target convergence and stability, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than generating arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}. This is precisely the shortcoming associated with LfD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning.

\subsection{\textcolor{red}{Approaches that tackle the joint+task problem}}
\textcolor{red}{*See comments in tex*}
% TO YO:
% ADD THESE THREE REFERENCES HERE AND SUMMARIZE THEM
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

\cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two. However, this approach no longer guarantees convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian.

\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions.

\subsection{Our proposed Approach}
\textcolor{red}{Dynamical System, Why?\\Linear Parameter Varying, Why?\\Lower-Dimensional Manifold, Why?\\}
In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. In this work, we depart from any modulation or combination of DS and instead propose a novel dynamical system which:

\begin{enumerate}[leftmargin=*]
\item computes a \begin{bf}complex motion in joint space\end{bf} that provably and stably converges to a \begin{bf}fixed task-space target\end{bf}.
\item \textbf{avoids} the need for computing \textbf{pseudo-inverses}, and cleanly moves through kinematic ``singularities".
\item is formulated such that complex \textbf{joint-space behaviors} can be \textbf{learned} from demonstrations in \textbf{synergy space}.
\end{enumerate}

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics
method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is the first known work to employ a JT system to learn behaviors from demonstrations. 
%while obeying the robots kinematic constraints.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=0.95\linewidth,trim={0 20 450 0},clip]{Pic/Schematic.jpg}
%\includegraphics[width=0.9\linewidth,trim={580 20 0 0},clip]{Pic/Schematic.jpg}
%\caption{ Standard control architecture using Cartesian dynamical systems (DS)\textbf{(top)}  and our proposed approach \textbf{(bottom)}.}
%\label{fig:schematic}
%\end{figure}
\section{Problem Statement} \label{Sec:Prob}
Consider a robotic system with $d$ task-space dimensions and $m$ degrees of freedom. We direct the system using a joint position or joint velocity controller, which can have joint position limits and a maximum joint velocity. We are further provided with a set of $N$ demonstrated joint-space trajectories $D=\{\{q_{t,n},\dot{q}_{t,n}\}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$, where $T_n$ is the number of the sample points of the $n^{\text{th}}$ demonstration. We refer to the system's joint-space position as $q=\begin{bmatrix} q^1 & \dots & q^m
\end{bmatrix}^T \in \mathbb{R}^m$, and to its task-space position as $x\in \mathbb{R}^d$.\footnote{For sake of brevity and simplicity, the time index, $t$, is dropped throughout the paper. } The kinematics of the robot are assumed to be known, hence, the robot's forward kinematics is indicated by $x = H(q)$ and its Jacobian is $J(q) = \frac{dx}{dq}\in \mathbb{R}^{m\times d}$.\\
We wish to formulate a dynamical system $\dot{q} = f(q)$ which satisfies the following two criteria:
\renewcommand{\labelenumi}{(\Roman{enumi})}
\begin{enumerate}
\item The dynamical system must be Lyapunov stable\footnote{Unless otherwise specified, "stability" in this paper always refers to global Lyapunov stability. We make no claim to proving global asymptotic stability, which is in fact impossible to achieve in a joint-constrained kinematic system. For example, any finite-size manipulator will always have regions beyond its reach that it cannot converge to.} with respect to a fixed task-space target $x^*$. This can be expressed by ensuring that the following Lyapunov function
\begin{equation}
V(q) = (H(q) - x^*)^TP(H(q) - x^*) 
\label{eq:Lyp}
\end{equation}
is stable; i.e. $\dot{V}(q)\leq0 ~\forall q\in Q$ and $V(q)=0~ \forall q\in Q^*$. Where  $Q=\{q|q^i_{min} < q^i < q^i_{max},~\forall i\in \{1,\dots,d\}\}$ and $Q^*=\{q|H(q)=x^*\wedge q\in Q\}$. $P\in \mathbb{R}^{d\times d} $ is a symmetric and positive definite matrix. $V(.)$ can be thought of as a metric for the task-space distance-to-go.
\item The dynamical system should encapsulate the desired joint-space behaviors such that the following metric is minimized
\begin{equation}
\vspace{-5pt}
e_{total} = \frac{1}{NT_n}\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d; t,n} - f(q_{t,n}) \right \|
\label{eq:optim_error}
\end{equation}
  where $\dot{q}_d$ is the desired ``true" velocity, and $f(\cdot)$ is the motion generation policy.
\end{enumerate}

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
\textcolor{red}{Change semi-definite to definite everywhere\\Change overall $A(q)$ to $\mathcal{A}(q)$\\ Introduce 'behavior synergies' here\\}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \ref{eq:Lyp} and \ref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -A(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $A(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $A(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
A(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{Pic/A_comparison_positions.pdf}
\caption{Three example 3-DOF motions (A, B, C), each with a different constant joint augmentation matrix $A$ (emphasizing the hip, knee, and ankle respectively), A: $A(q)=diag(5,1,1) $, B: $A(q)=diag(1,5,1)$, and C: $A(q)=diag(1,1,5)$. On the left, the task-space traces of each motion. On the right, the time-scaled joint positions of each joint. Each motion tends to use its ``primary" joint most and uses the other available joints to compensate for what the primary joint cannot do.}
\label{fig:A_example}
\vspace{-15pt}
\end{figure}

Before proving that the proposed dynamical system satisfies all of the criteria, let us establish an intuitive understanding of the components of the system. While it may seem daunting at first, each of the elements has a straightforward explanation. One can intuitively understand the control law as follows: $(H(q) - x^*)$ denotes the position error w.r.t. the task target (warped according to P), and by multiplying that error by the transposed Jacobian $J^T(q)$, the error is projected into joint space (similar to Jacobian transpose control \cite{wolovich1984computational,sciavicco1988solution}). The positive semi-definite matrix $A(q)$ warps the resulting joint-space velocity; Fig. \ref{fig:A_example} illustrates the effects of  $A(q)$ on the generated motion. Thus the controller can be thought of as a proportional controller in joint space. Lastly, we refer to the $P$ matrix as the \begin{bf} task augmentation matrix \end{bf}(because it augments the task error, and thus the direction of motion) and $A(q)$ as the \begin{bf} joint augmentation matrix \end{bf} (because it augments the outputted joint velocities).
%When using each of these matrices, the controller will augment the joint velocities to favor using one joint more than the others (in $A_1$ the hip, in $A_2$ the knee, and in $A_3$ the ankle). This ''augmentation" is simply a matrix multiplication ($A\dot{q}_{raw}$). The components of the outputted velocity are linear combinations of the ''raw" un-augmented joint velocities, where the entries in $A$ define the precise ratios. We can see the joint positions resulting from our experiment over time on the right side of Fig. \ref{fig:A_example}. Each motion tends to use its ``primary" joint most (the joint where the velocity is heavily scaled up) and uses the other available joints to compensate for what the primary joint cannot do. For example, Motion 1 starts out using mostly the hip, but once moving the hip no longer brings the system closer to the goal, the system uses the other joints to fold inwards and reach the goal. Ultimately, all three controllers converge on their target, but each has a different path through joint space depending on which joints we choose to emphasize in the behavior matrix $A$. The off-diagonal terms of $A$ have a more nuanced contribution; e.g. $A_{1,2}$ defines the amount that elbow velocity should be converted into hip velocity.

\newtheorem{prop1}{Proposition}
\begin{prop1}
\label{prop:stability}
The flow of motion generated by the dynamical system \eqref{eq:ds} accomplishes criteria (I) if \eqref{eq:ds} meets the following constraints.

>>>>

\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{url}
\usepackage[font={footnotesize}]{caption}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[usenames, dvipsnames]{color}
\usepackage{amsmath}
\renewcommand{\labelenumii}{\Roman{enumii}} 
\usepackage{authblk}
\usepackage{hyperref}
% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Learning Joint-Space Stable Dynamical Systems for Task-Space Objectives}
\title{The Augmented Joint-space Task-oriented Dynamical System}

%
%
\author{Yonadav~Shavit*,  Seyed~Sina~Mirrazavi~Salehian*, Nadia~Figueroa*, Aude~Billard
% <-this % stops a space
\thanks{*These authors contributed equally to this work.}
\thanks{Y. Shavit is with the Department
of Electrical Engineering and Computer Science, Massachusetts Institute of Technology, Cambridge,
MA, 02139 USA. E-mail: yonadav@mit.edu.}% <-this % stops a space
\thanks{S. S. M. Salehyan, N. Figueroa, and A. Billard are with the Swiss Federal Institute of Technology (EPFL), 1015 Lausanne, Switzerland. \\E-mail: \{sina.mirrazavi,nadia.figueroafernandez,aude.billard\}@epfl.ch.}
}% <-this %

@@

\begin{abstract}
In this paper, we propose a stable joint-space dynamical system that captures desired behaviors in joint-space while converging towards a reachable target in task-space with respect to the robot's kinematic constraints. Our method is fast to compute and smoothly moves through classic kinematic singularities by avoiding the use of the pseudo-inverse Jacobian; moreover, we prove that it stably moves towards its target and is guaranteed to obey the robot's kinematic joint limits. To encode complex joint-space behaviors while meeting these stability criteria, the dynamical system is constructed as a Linear Parameter Varying (LPV) system, enabling us to encode complex joint-space behaviors. We propose a method to train such complex behaviors from kinesthetic demonstrations, by learning the parameters of the LPV system. We begin by applying a latent-embedding and a probabilistic approach to discover and represent a set of local behaviors from the demonstrated motions. Then, the corresponding local joint-space behaviors are estimated by solving a convex semi-definite optimization problem that minimizes the joint velocity error from the demonstrations. The effectiveness of our approach is illustrated by a variety of motions for a 7-DOF KUKA LWR4+ robot arm.\end{abstract}

@@

\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:intro}
Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 14.0cm},clip]{Without_Obstcle.jpg}
\includegraphics[scale=.23,trim={0 0 0 9.cm},clip]{With_Obstcle.jpg}
\caption{Two possible robot motions in joint space accomplishing the same behavior in task-space (pouring chips in a bowl). Though the \textcolor{cyan}{\textbf{task-space trajectories}} are similar, the \textcolor{orange}{\textbf{joint-space trajectories}} are different; e.g. the bottom example moves in joint-space to avoid an obstacle that the top one does not.}
\label{fig:robot_example}
\vspace{-1.0cm}
\end{figure}

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{Pic/Schematic.jpg}
\caption{A simplified schematic comparing the standard control architecture using Cartesian dynamical systems (right) and our propose approach. By integrating the "inverse kinematic (IK) solver" and "motion generator" blocks into a unified block, the proposed approach not only eliminates undesirable effects of the IK solver but also is capable of generating motions that satisfy the kinematic constraints of the robot.}
\label{fig:schematic}
\vspace{-0.8cm}
\end{figure*}

@@

Although DS-based task-space learning techniques ensure target convergence and stability, an advantageous feat within the PbD paradigm, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than blindly choosing the arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}.

This is precisely the shortcoming associated with PbD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning. \cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two. However, this approach no longer guarantees convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian. \cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions.

In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JTDS) that not only complies with the task-space constraints, but also avoids the problems generated by pseudo-inverse approximations and takes into consideration the robot's kinematic limits, see Fig. \ref{fig:schematic}. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities and joint kinematic limits. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations and joint limits via online modulation. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. In this paper we depart from any modulation or combination of DS and instead propose a novel dynamical system which:

\begin{enumerate}
\item computes a \begin{bf}motion in joint space\end{bf} that provably stably moves to a \begin{bf}fixed task-space target\end{bf} in a single DS.
\item inherently obeys \textbf{kinematic joint limits}.
\item \textbf{avoids} the need for computing \textbf{pseudo-inverses}, and cleanly moves through kinematic "singularities".
\item is formulated such that it can \textbf{learn} complex \textbf{joint-space behaviors} from demonstrations.
\end{enumerate}

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics
method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work integrating discontinuous joint limits \cite{sciavicco1988solution} and designing velocity adjustments by hand \cite{Shi2016}, this is the first known work to employ a JT system to learn behaviors from demonstrations while obeying the robots kinematic constraints.

@@

\section{Problem Statement} \label{Sec:Prob}
Consider a robotic system with $d$ task-space dimensions and $m$ degrees of freedom. We direct the system using a joint position or joint velocity controller, which can have joint position limits and a maximum joint velocity. We are further provided with a set of $N$ demonstrated joint-space trajectories $D=\{\{q_{t,n},\dot{q}_{t,n}\}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$, where $T_n$ is the number of the sample points of the $n^{\text{th}}$ demonstration. We refer to the system's joint-space position as $q=\begin{bmatrix} q^1 & \dots & q^m
\end{bmatrix}^T \in \mathbb{R}^m$, and to its task-space position as $x\in \mathbb{R}^d$.\footnote{For sake of brevity and simplicity, the time index, $t$, is dropped throughout the paper. } The kinematics of the robot are assumed to be known, hence, the robot's forward kinematics is indicated by $x = H(q)$ and its Jacobian is $J(q) = \frac{dx}{dq}\in \mathbb{R}^{m\times d}$.\\
We wish to formulate a dynamical system $\dot{q} = f(q)$ which satisfies the following criteria:
\renewcommand{\labelenumi}{(\Roman{enumi})}
\begin{enumerate}
\item The dynamical system must be Lyapunov stable\footnote{Unless otherwise specified, "stability" in this paper always refers to global Lyapunov stability. We make no claim to proving global asymptotic stability, which is in fact impossible to achieve in a joint-constrained kinematic system. For example, any finite-size manipulator will always have regions beyond its reach that it cannot converge to.} with respect to a fixed task-space target $x^*$. This can be expressed by ensuring that the following Lyapunov function
\begin{equation}
V(q) = (H(q) - x^*)^TP(H(q) - x^*) 
\label{eq:Lyp}
\end{equation}
is stable; i.e. $\dot{V}(q)\leq0 ~\forall q\in Q$ and $V(q)=0~ \forall q\in Q^*$. Where  $Q=\{q|q^i_{min} < q^i < q^i_{max},~\forall i\in \{1,\dots,d\}\}$ and $Q^*=\{q|H(q)=x^*\wedge q\in Q\}$. $P\in \mathbb{R}^{d\times d} $ is a symmetric and positive definite matrix. $V(.)$ can be thought of as a metric for the task-space distance-to-go.
\item The dynamical system must respect the kinematic joint constraints of the robot:
\begin{equation}
q(0)\in Q \rightarrow q(t)\in Q~~~~\forall t>0~
\end{equation}
\item The dynamical system should encapsulate the desired joint-space behaviors such that the following metric is minimized
\begin{equation}
\vspace{-5pt}
e_{total} = \frac{1}{NT_n}\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d; t,n} - f(q_{t,n}) \right \|
\label{eq:optim_error}
\end{equation}
  where $\dot{q}_d$ is the desired ``true" velocity, and $f(\cdot)$ is the motion generation policy.
\end{enumerate}

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the three criteria presented in (I), (II), (III).
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -\mathcal{A}(q)J^T(q)P(H(q) - x^*)
\end{equation}
where 
\begin{equation}
\label{eq:SAS}
\mathcal{A}(q) = S(q) A(q) S^T(q). 
\end{equation}
$S(q)=diag(s^1(q),\dots,s^d(q))$ is a diagonal matrix and $ s^i(\cdot)\in C^0~\forall i \in \{1,\dots d\} $. $A(q)\in \mathbb{R}^{d\times d}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $A(q)$ is a nonlinear combination of constant linear matrices, each of which encodes a local joint-space behavior. 
\begin{equation}
\label{eq:A_def}
A(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{d\times d} $ and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are constant matrices and the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability and convergence proof can easily be extended for $\theta_k (t, q(t), d(t))$.} representing each local behavior, respectively. Based on \eqref{eq:ds}, one can enforce different local joint behaviors in different regions, and compose them to create a more complex multi-behavior motion.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{Pic/A_comparison_positions.pdf}
\caption{Three example 3-DOF motions (A, B, C), each with a different constant behavior matrix $\mathcal{A}$ (emphasizing the hip, knee, and ankle respectively), A: $\mathcal{A}(q)=diag(5,1,1) $, B: $\mathcal{A}(q)=diag(1,5,1)$, and C: $\mathcal{A}(q)=diag(1,1,5)$. On the left, the task-space traces of each motion. On the right, the time-scaled joint positions of each joint (with each color signifying a different trajectory). Each motion tends to use its ``primary" joint most and uses the other available joints to compensate for what the primary joint cannot do.}
\label{fig:A_example}
\vspace{-15pt}
\end{figure}

Before proving that the proposed dynamical system satisfies all of the criteria, let us establish an intuitive understanding of the components of the system. While it may seem daunting at first, each of the elements has a straightforward explanation. One can intuitively understand the control law as follows: $(H(q) - x^*)$ denotes the position error w.r.t. the task target (warped according to P), and by multiplying that error by the transposed Jacobian $J^T(q)$, the error is projected into joint space (similar to Jacobian transpose control \cite{wolovich1984computational,sciavicco1988solution}). The positive semi-definite matrix $\mathcal{A}(q)$ warps the resulting joint-space velocity; Fig. \ref{fig:A_example} illustrates the effects of  $A(q)$ on the generated motion. Thus the controller can be thought of as a proportional controller in joint space. We refer to the $P$ matrix as the \begin{bf} task augmentation matrix \end{bf}(because it augments the task error, and thus the direction of motion) and $A(q)$ as the \begin{bf} joint augmentation matrix \end{bf} (because it augments the outputted joint velocities). Lastly, $S(q)$ intuitively enforces the joint constraints: as $q^i$ nears $q^i_{min}$, the velocity in that direction goes to $0$, and similarly when it nears $q^i_{max}$ the velocity goes to $0$.

%When using each of these matrices, the controller will augment the joint velocities to favor using one joint more than the others (in $A_1$ the hip, in $A_2$ the knee, and in $A_3$ the ankle). This ''augmentation" is simply a matrix multiplication ($A\dot{q}_{raw}$). The components of the outputted velocity are linear combinations of the ''raw" un-augmented joint velocities, where the entries in $A$ define the precise ratios. We can see the joint positions resulting from our experiment over time on the right side of Fig. \ref{fig:A_example}. Each motion tends to use its ``primary" joint most (the joint where the velocity is heavily scaled up) and uses the other available joints to compensate for what the primary joint cannot do. For example, Motion 1 starts out using mostly the hip, but once moving the hip no longer brings the system closer to the goal, the system uses the other joints to fold inwards and reach the goal. Ultimately, all three controllers converge on their target, but each has a different path through joint space depending on which joints we choose to emphasize in the behavior matrix $A$. The off-diagonal terms of $A$ have a more nuanced contribution; e.g. $A_{1,2}$ defines the amount that elbow velocity should be converted into hip velocity.

\newtheorem{prop1}{Proposition}
\begin{prop1}
\label{prop:stability}
The flow of motion generated by the dynamical system \eqref{eq:ds} accomplishes criteria (I) and (II), if \eqref{eq:ds} meets the following constraints.
